%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small#2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{xcolor}  % 这个宏包可以用于定义颜色
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,      
  urlcolor=cyan,
  citecolor=blue,
}

% 自定义的 \href 命令
\renewcommand{\href}[2]{\textcolor{blue}{\underline{#2}}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth} {l@{\extracolsep{\fill}}r}
  \textbf{\Large Weijie Shen} & \href{mailto:shenweijie98@gmail.com}{shenweijie98@gmail.com} $|$ \href{https://github.com/ywzz3293}{GitHub} \\
  +1(514)6904706 & \href{https://www.linkedin.com/in/weijie-shen-0a5668160/}{LinkedIn} $|$ \href{https://ywzz3293.github.io/protfolio-website/}{Portfolio} \\
\end{tabular*}

%----------Summary-----------------
\section{Summary}
\small
{C++-focused software engineer with 6+ years across backend systems, analytics tooling, and performance-sensitive applications. Main stack is C++11/14/17/20, with Python and some fullstack work when the product needs it. Most projects have involved code that has to stay fast, testable, and maintainable across large codebases.}
 
 
%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
 
\resumeSubheading
{OpenText}{Waterloo, ON}
{Senior Software Engineer (Full Stack)}{Apr 2025 -- Present}
\resumeItemListStart
  \resumeItem{AI Log Analysis \& RCA Automation}
    {Built a Copilot subagent workflow that pulls Jira tickets and related documents, filters them with team domain knowledge, runs AI-assisted log analysis, and sends RCA drafts to customer support. It is being shaped into a VM/cloud-hosted web service so support can handle common cases without waiting on developers.}
  \resumeItem{System Development}
    {Build and maintain C++ backend services and frontend administrative tools used around business-critical workflows.}
  \resumeItem{Design Collaboration}
    {Work with architects and product managers to sort out design dependencies before implementation. Complete high level and low level design document for monitoring system using grafana and prometheus.}
\resumeItemListEnd
 
 
\resumeSubheading
{Ansys (Synopsys)}{Vancouver, BC}
{R\&D Software Engineer II}{Oct 2021 -- Apr 2025}
\resumeItemListStart
  \resumeItem{Analytics Algorithm Development in C++}
    {Built analytics algorithms in modern C++ for GPU architecture evaluation, with strict latency and throughput targets on large datasets.}
  \resumeItem{Architecture \& Code Quality}
    {Refactored 1.5k source files into a decoupled MVC architecture using C++17 OOP patterns; Take ownership of untouched module and reduced regressions and bugs by 60\%.}
  \resumeItem{Automated Testing \& Cross-Platform Debugging}
    {Wrote automated regression and performance tests in Python and tracked down multi-platform defects across large codebases.}
  \resumeItemListEnd
 
\resumeSubheading
{LifeWorks (Telus Health)}{Montreal, QC}
{Software Analyst (Backend)}{Jun 2020 -- Jun 2021}
\resumeItemListStart
  \resumeItem{Performance Optimization \& Code Quality}
    {Reduced system processing time by 15\% through targeted algorithmic optimizations; led code reviews during production migration to C\#/.NET Core.}
  \resumeItemListEnd
 
\resumeSubheading
{Autolog}{Montreal, QC}
{Computer Vision Engineer}{Jan 2019 -- Feb 2020}
\resumeItemListStart
  \resumeItem{Object Detection in C++}
    {Wrote a multi-threaded object detection algorithm in C++ for real-time throughput.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
 
%---------- Technical Skills ----------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages \& Standards}
{C++ (C++11/14/17/20), Python, TypeScript, JavaScript, Angular, Java, C\#, Rust; OOP, design patterns, data structures \& algorithms}
\resumeSubItem{Tools \& Practices}
{Git, Bitbucket, Jira, Bitbucke, Confluence, MS Visual Studio, VS Code, SonarQube, GitHub CoPilot, CI\/CD, Agile/Scrum, test automation, performance profiling}
\resumeSubHeadingListEnd
 
%---------- Projects ----------
\section{Technical Projects}
\resumeSubHeadingListStart
\resumeSubItem{Multithreaded Server (Windows \& Linux)}
{C++ server built to run the same way on Windows and Linux, with unit and integration tests covering both platforms.}
\resumeSubItem{AWS Inventory Management}
{Next.js/Node.js inventory application with Redux caching and AWS EC2/S3/RDS for persistence. Added automation around data sync and workflow-heavy tasks.}
\resumeSubHeadingListEnd
 
%---------- Education ----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{École Polytechnique de Montréal}{Montreal, QC}
{Master of Engineering}{2018}
\resumeSubHeadingListEnd
 
\end{document}